Learning \strips\ action models from {\em state-invariants}

### 2019-02-07 doc/ijcai-19-deductivelearning/deductivelearning.tex
bib updates to the ijcai19 paper on deductive learning

\begin{abstract}
This paper addresses the learning of action models from {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient learning examples. Our approach is built on top of a {\em classical planning} compilation that is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. The experimental results show that, at unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} are helpful to learn better \strips\ action models.
\end{abstract}

@@

The specification of planning action models is a complex process that limits, too often, the application of {\em model-based planning} systems to real-world tasks~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve the {\em knowledge acquisition bottleneck} of planning and nowadays, there exists a wide range of effective approaches for learning action models~\cite{arora:amodels:ker2018}. Many of the most successful approaches for learning planning action models are however purely {\em inductive}~\cite{yang2007learning,pasula2007learning,mourao2010learning,zhuo2013action}, meaning that their performance is linked to the {\em amount} and {\em quality} of the input examples (namely observations of plan executions generated by the aimed action model).

This paper addresses the learning of action models from a different source of knowledge, {\em deductive} knowledge, with the form of {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient input observations. Given an action model, state-of-the-art planners infer {\em state-invariants} from that model to reduce the planner search space and make the planning process more efficient~\cite{helmert2009concise}. In this paper we follow the opposite direction and leverage {\em state-invariants} to learn a planning action model.

Our approach extends the {\em classical planning} compilation for learning \strips\ action models~\cite{aineto2018learning}. Our extension is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. The experimental results show that, at unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} help to learn better \strips\ models with the {\em classical planning} compilation.

@@

>>>>

\begin{abstract}
This paper addresses the learning of action models from {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to cushion the negative impact of insufficient learning examples. Our approach is a {\em classical planning} compilation that is flexible to different kinds of input knowledge (e.g., partially observations of plan executions including partially observed intermediate states and/or actions) and outputs an action model that is {\em consistent} with the given input knowledge. The experimental results show that, even at unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} are helpful to learn better \strips\ action models.
\end{abstract}

@@

The specification of planning action models is a complex process that limits, too often, the application of {\em model-based planning} systems to real-world tasks~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve the {\em knowledge acquisition bottleneck} of planning and nowadays, there exists a wide range of effective approaches for learning action models~\cite{arora:amodels:ker2018}. Many of the most successful approaches for learning planning action models are however purely {\em inductive}~\cite{yang2007learning,pasula2007learning,mourao2010learning,zhuo2013action}, meaning that their performance is linked to the {\em amount} and {\em quality} of the input examples (which normally are observations of plan executions generated by the aimed action model).

This paper addresses the learning of action models exploiting a different source of knowledge, {\em deductive} knowledge, with the form of {\em state-invariants} (i.e. logic formulae that specify constraints about the possible states of a given domain) to cushion the negative impact of insufficient learning examples. Given an action model, state-of-the-art planners infer {\em state-invariants} from that model to reduce search spaces and make the planning process more efficient~\cite{helmert2009concise}. In this paper we follow the opposite direction and leverage {\em state-invariants} to learn the planning action model.

Our approach for learning \strips\ action models from {\em state-invariants} is building a classical planning compilation that is inspired by recent work by~\citeauthor{aineto2018learning}~\citeyear{aineto2018learning}. Our compilation is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. The experimental results show that, even at unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} help to learn better \strips\ models with the {\em classical planning} compilation.

@@

{\em State-invariants} have been previously used to infer a HTN planning model~\cite{lotinac2016constructing}.
